\RequirePackage[l2tabu, orthodox]{nag}

\documentclass[a4paper, 11pt]{article}

\usepackage{microtype} % Slightly tweak font spacing for aesthetics
%\usepackage{gfsdidot}
\usepackage[ampersand]{easylist}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage[a4paper, margin=1.in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{changepage} 
\usepackage[
giveninits=true,
doi=false,
isbn=false,
url=false,
citestyle=phys,
					]{biblatex}
\DeclareNameAlias{author}{last-first}

\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}

\title{}
\author{}
\date{Last Edited: \today}

\newcommand{\myrule}{\hrulefill}
\newcommand{\noi}{\noindent}
\newcommand{\ind}{\indent}

\newenvironment{pari}{\begin{adjustwidth}{15 pt}{}}{\end{adjustwidth}}

\begin{document}

\begin{center} 
\textbf{Dylan Cromer} 
\\
\myrule
\end{center}

\noi Cornell University \hfill website: \texttt{dylancromer.com}
\\
Department of Astronomy \hfill email: \texttt{dylan@dylancromer.com}
\\
516 Space Sciences Building \hfill
\\
Ithaca, NY 14853 \hfill
\\
phone: 607-255-8925 \hfill
\\
university email: \texttt{dmc396@cornell.edu} \hfill
\\

\fancyfoot{\myrule \\ Dylan Cromer \hfill \thepage}

\noi \textbf{Research Interests}
\\

\noi \textbf{Primary Interests:} Cosmology, inferring fundamental physics from cosmological observations, physics and mathematics education/pedagogy.
\\

\noi \textbf{Other Interests:} Mathematics of path integrals in quantum field theory and beyond, mathematics applied to political science and sociology, fast radio bursts, computer visualization of relativity.
\\

\noi \textbf{Education}
\begin{itemize}[leftmargin=*]
\item Astronomy PhD Program. \emph{Cornell University}. 2017 -- present.
	\item \noi B.S. in Physics, B.A. in Mathematics. \emph{UNC-Asheville}. 2013 -- 2017 (summa cum laude, distinction as research scholar). 
	\item \noi High-school diploma, \emph{Homeschooled}. --2013.
	\\
\end{itemize}

\noi \textbf{Employment History}
\begin{itemize}[leftmargin=*]
	\item \noi \emph{Graduate Research Assistant at Cornell University}. August 2017 -- May 2018.
	\begin{pari}
		Supervised by Professor Rachel Bean. Project on modifying correlation functions for enhanced signal-to-noise properties from galaxy surveys.
	\end{pari}

	\item \noi \emph{STEM Outreach Intern at UNC-Asheville Department of Physics}. August 2016 -- May 2017.
	\begin{pari}
		Physics and general scientific outreach position. Assisted outreach events in coordination with Asheville City Schools Foundation IRL Program. Assisted North Carolina Section American Association of Physics Teachers Fall 2016 meeting.
	\end{pari}

	\item \noi \emph{Lookout Observatory Docent at UNC-Asheville.} August 2014 -- May 2017
		\begin{pari}
			\noi Assisted in monthly public stargazes, outreach events, and other programs held by the observatory.
		\end{pari}

	\item \noi \emph{Physics Peer Tutor at UNC-Asheville Peer Tutoring Program}. July 2014 -- May 2017.
	\begin{pari}
	\noi Tutor for introductory mechanics and electromagnetism courses, have occasionally tutored students from upper-level physics courses.
	\end{pari}

	\item \noi \emph{Math Tutor at UNC-Asheville Math Assistance Center}.  September 2016 -- May 2017.
	\begin{pari}
		\noi Tutor for math courses taught at UNC-Asheville. 
	\end{pari}
\end{itemize}

\newpage

\noi \textbf{Published Articles}
\\

\noi "Surface Enhancement in Ferroelectric Lithographic Silver Nanowires", 
\\
	\ind \emph{National Conferences on Undergraduate Research 2016 Proceedings}, 1055--1063.
\\

\noi \textbf{Conference and Symposium Presentations}
\\

\noi \textbf{Talks}
\\

\noi "Fast Radio Bursts - Mysterious Flashes From Other Galaxies, or Our Own?", Sparks Lecture Series seminar, UNC-Asheville, Asheville, NC, February 2017.
\\

\noi "Computational Modeling of Surface Enhancement in Ferroelectric Lithographic Nanowires", National Conferences on Undergraduate Research, UNC-Asheville, Asheville, NC, April 2016.
\\

\noi \textbf{Selected Poster Presentations}
\\
\emph{Repeated poster presentations have been omitted.}
\\

\noi "Computational Modeling of Surface Enhancement", UNC-Asheville Undergraduate Research Symposium, Asheville, NC, December 2016.
\\

\noi "Comparing Fast Radio Burst Observations to a Stellar Flare Model", North Carolina Section of the American Association of Physics Teachers and Society of Physics Students Joint Meeting, UNC-Asheville, Asheville, NC, November 2016.
\\

\noi "Modeling Surface-Enhanced Raman Spectroscopy via Computational Electrodynamics", 2016 Quadrennial Physics Congress, San Francisco, CA, November 2016.
\\

\noi "First Steps in Comparing Analytical Surface Enhancement Models With Experimental Results", State of North Carolina Undergraduate Research and Creativity Symposium, High Point University, High Point, NC, November 2015.
\\

\noi "Modeling Surface Enhancement due to Silver Nanowires", UNC-Asheville Undergraduate Research Symposium, Asheville, NC, April 2015.
\\

\noi "Modeling Fast Radio Bursts in Stellar Coronae", UNC-Asheville Undergraduate Research Symposium, Asheville, NC, April 2015.
\\

\noi "Spatially Variable Surface Enhancement of
Ferroelectric Lithographic Nanowires", UNC-Asheville Undergraduate Research Symposium, Asheville, NC, December 2014.
\\

\noi "Modeling Fast Radio Bursts in Stellar Coronae", State of North Carolina Undergraduate Research and Creativity Symposium, North Carolina State University, Raleigh, NC, November 2014.
\\

\noi \textbf{Selected Outreach Activities}
\\

\noi Volunteer, Alien Worlds workshop, Cornell University Expanding Your Horizons program, April 2018.
\\

\noi Volunteer, "Museum In the Dark", Museum of the Earth, Ithaca NY, October 2017.
\\

\noi Ran UNC-Asheville Society of Physics Students scientific outreach workshop, February 2017.
\\

\noi Event leader, Junior Bulldog Program, UNC-Asheville, fall 2016. 
\\

\noi "Event Captain" volunteer, North Carolina Science Olympiad, February 2016.
\\

\noi "Event Captain" volunteer, North Carolina Science Olympiad, February 2015.
\\

\noi Assistant volunteer, North Carolina Science Olympiad, February 2014.
\\

\noi Volunteer, Super Saturday enrichment program, UNC-Asheville; fall 2013, spring 2014, and fall 2014.
\\


\noi \textbf{Computing Experience} 
\\

\noi Python 3 -- extensive usage for scripting in scientific context. Familiar with most common scientific/numeric packages.
\\

\noi Mathematica -- extensive usage for coursework, wrote program to assist in fast radio burst research.
\\

\noi \LaTeX \, -- extensive usage for coursework, academic writing.
\\

\noi Linux/Unix -- familiar with setting up and using several flavors of Linux. Used for both desktop and server applications.
\\

\noi \textbf{Awards, Grants, and Scholarships}
\\

\noi Cornell Graduate Fellowship, awarded for 2017--2018 academic year, deferred until 2018--2019.
\\

\noi Manly E. Wright Scholarship Award recipient, UNC-Ashevile, class of 2017.
\\

\noi UNC-Asheville Mathematics Department Parsons Scholarship, 2016--2017 academic year.
\\

\noi North Carolina Space Grant Research Scholarship, summer 2015. Awarded for fast radio burst research project.
\\

\noi UNC-Asheville Physics Department research stipend, summer 2014. Funds granted for fast radio burst research project.
\\

\noi North Carolina Space Grant Student Scholarship, 2014--2015 academic year.
\\


\noi \textbf{Academic Organizations}
\\

\noi Society of Physics Students. Outreach coordinator for UNC-Asheville Chapter.
\\

\noi Sigma Pi Sigma, inducted member (physics honors society).
\\

\noi UNC-Asheville Honors Program.

\end{document}
